A generalized definition of multidimensional item response theory parameters

### 2024-09-03 output/paper_draft/paper_M2PLM_parameters.Rmd
Drops "methods" and "results" titles

# Method

## Model formulation

@@

## Linear algebra of non-orthogonal coordinates

@@

### Test space definition

@@

### Direction cosines in the latent space

@@

## Model recasting into polar coordinates

@@

## Point of maximum slope

@@

# Results

## Relationship between test space and latent space

@@

## Generalized multidimensional parameters

@@

### Agnostic version

@@

### Covariance-based version

@@

### Correlation-based version

@@

## Vector representation

@@

### Geometric properties of the items

@@

## Graphical representation

@@

### Graphical representation example

@@

## Application to examples from the literature

@@

### @reckase_multidimensional_2009

@@

### @tezza_modelo_2018

>>>>

# Model formulation

@@

# Linear algebra of non-orthogonal coordinates

@@

## Test space definition

@@

## Direction cosines in the latent space

@@

# Model recasting into polar coordinates

@@

# Point of maximum slope

@@

# Relationship between test space and latent space

@@

# Generalized multidimensional parameters

@@

## Agnostic version

@@

## Covariance-based version

@@

## Correlation-based version

@@

# Vector representation

@@

## Geometric properties of the items

@@

# Graphical representation

@@

## Graphical representation example

@@

# Application to examples from the literature

@@

## @reckase_multidimensional_2009

@@

## @tezza_modelo_2018
